---
title: "HW2 Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(btry6520fns)
```

## Leveraging Examples

Here's a plot of the two different types of algorithmic leveraging. Pretty clearly, this is random data so there should be no effects, but the uniform leveraging procedure seems to pick up a higher variance of effects than hat based leveraging.

```{r}
X = matrix(rnorm(10000), ncol = 20)
y = rnorm(nrow(X))

# algorithmic leveraging
hat_lev = algo_leverage(y, X, size = 100, method = "hat")

# uniform leveraging
unif_lev = algo_leverage(y, X, size = 100, method = "uniform")

plot(hat_lev, unif_lev)
```

## Elastic net coordinate descent

Here's an example of medium n, large p (it's not ImageNet but it's okay...)

```{r}
data = gen_fs_system(n = 100, p = 500)
beta_pred = elnet_coord(data$y, data$x, lambda = 0.5, alpha = 0.5)

# we're able to pick up the true components in even a large p system
print(data$beta[1:7] - beta_pred[1:7])

# number of nonzero elements
print(sum(beta_pred > 0))
```

## solving OLS systems

```{r}
A = gen_tridiag_mat(4, n = 100) #generate a tridiagonal matrix
v = rep(c(1, 0), nrow(A) / 2)
b = A %*% v

jac_soln = solve_ols(A, b, nIt = 100, method = "Jacobi", parallel = FALSE)
jac_error = sum(jac_soln - v)
print(jac_error)

gs_soln = solve_ols(A, b, nIt = 100, method = "GS", parallel = FALSE)
gs_error = sum(gs_soln - v)
print(gs_error)

print("Times")
print(attr(jac_soln,"elapsed_time"))
print(attr(gs_soln,"elapsed_time"))
```

```{r}
# commented bc roxygen doesn't like the parallel functionality
# A = gen_tridiag_mat(4, n = 100) #generate a tridiagonal matrix
# v = rep(c(1, 0), nrow(A) / 2)
# b = A %*% v
# 
# jac_soln = solve_ols(A, b, nIt = 100, method = "Jacobi", parallel = TRUE)
# jac_error = sum(jac_soln - v)
# print(jac_error)
# 
# print(attr(jac_soln,"elapsed_time"))
```
